---
title: "Using ezPurrr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using-ezPurrr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ezPurrr)
library(tidyverse)
```


Create a nested dataset. 
```{r}
nest_df <- palmerpenguins::penguins %>%
  #group_by(species, island, sex, year) %>%
  group_by(island, species) %>%
  nest()

head(nest_df)
```

### `sample_*()` methods.

sample_row() returns one random or one particular row (with `index` argument) from the nested dataset as a list. The first item of the list is the grouping variable, and the second item of the list is the dataset.
```{r}
nest_df %>% sample_row()

nest_df %>% sample_row(index = 3)
```

sample_data() returns one random or one particular data column (with `index` argument) from the nested dataset. This is the same as the first item from the list that was produced by `sample_row()`.
```{r}
nest_df %>% sample_data()

nest_df %>% sample_data(index = 3)
```

sample_group() returns one random or one particular grouping columns (with `index` argument) from the nested dataset.This is the same as the second item from the list that was produced by `sample_row()`.
```{r}
nest_df %>% sample_group()

nest_df %>% sample_group(index = 3)
```

### broadcst

You can use the sampling dataset to test the code you want to be applied for each row, such as figures or `lm()` models.

Plotting:
```{r}
nest_df %>% 
  sample_data(index = 3) %>% 
  ggplot(aes(x = bill_length_mm,
                           y = bill_depth_mm,
                           color = body_mass_g)) +
  geom_point()
```

Then, by wrapping it into a function, it can be easily broadcasted into each row of the nested dataset. 

```{r}
plotting <- function(data){
  data %>% ggplot(aes(x = bill_length_mm,
                             y = bill_depth_mm,
                             color = body_mass_g)) +
    geom_point()
}

broadcasted_df = nest_df %>% broadcast(plotting)

broadcasted_df$output[[1]]

```

You can also use it for modeling:
```{r}
tmp_df = nest_df %>% 
  sample_data(index = 3)

lm(body_mass_g ~ bill_length_mm * bill_depth_mm, data = tmp_df)

modeling <- function(data){
   lm(body_mass_g ~ bill_length_mm + bill_depth_mm, data = data)
}

nest_df %>% broadcast(modeling) %>% .$output

```

Instead of a list, you can also make the output a number (double).
```{r}

modeling <- function(data){
  model = lm(body_mass_g ~ bill_length_mm + bill_depth_mm, data = data)
  model$coefficients[2] # the slope for bill_length_mm
}

nest_df %>% broadcast(modeling) %>% .$output
```






```{r eval=FALSE, include=FALSE}
#This is just and example code chunk where Daniel was playing with the package.

library(palmerpenguins)
library(purrr)
library(dplyr)
library(ggplot2)
library(ezPurrr)

nested_d <- penguins %>% 
  nest_by(species) 

ex_data <- nested_d %>% 
  sample_data()

ggplot(ex_data, aes(sex, flipper_length_mm)) +
  geom_boxplot(aes(fill = sex)) +
  guides(fill = "none") +
  theme_minimal()

# wrap in a function
p <- function(d) {
  ggplot(d, aes(.data$sex, .data$flipper_length_mm)) +
    geom_boxplot(aes(fill = .data$sex)) +
    guides(fill = "none") +
    theme_minimal()
}

# this doesn't seem to work
#broadcast(nested_d, p)

# this does, so I would have expected the above to
map(nested_d$data, p)

# try a second one
ex_data %>% 
  filter(bill_length_mm > 50) %>% 
  select(bill_length_mm, bill_depth_mm) %>% 
  cor() 

# wrap in function
f <- function(d) {
  d %>% 
    filter(.data$bill_length_mm > 50) %>% 
    select(.data$bill_length_mm, .data$bill_depth_mm) %>% 
    cor() 
}
# broadcast(nested_d, f) # also doesn't work
map(nested_d$data, f) # this does

# Me messing about with quosures unsuccessfully 
# tmp <- quo(
#   data %>% 
#     filter(bill_length_mm > 50) %>% 
#     select(bill_length_mm, bill_depth_mm) %>% 
#     cor()
#   )
# 
# tmp
# 
# library(rlang)
# expr <- quo_get_expr(tmp)
# chr_expr <- gsub("ex_data", "data", expr)
# expr <- parse_expr(paste0(parse_exprs(chr_expr[-1]), collapse = " %>% "))
# 
# map(nested_d, !!tmp)
```
